PMV: Comparing the prediction accuracy of ISO 7730:2005 and ASHRAE 55:2023

### 2023-09-12 Manuscript/src/sections/titleAbstract.tex
feat: finalised second draft to send to Stefano

    \begin{abstract}
        The \ac{pmv} model was developed by Fanger more than 50 years ago to predict the mean thermal sensation of a group of people. 
        It is based on a heat balance model of the human body.

        \gls{55} states that the model can be used to determine ``the combinations of indoor thermal environmental factors and personal factors that will produce satisfactory thermal environmental conditions for a majority of the occupants within the space''.

        Being relatively simple to calculate and being included in both the \gls{7730} and \gls{55} Standards, the \ac{pmv} has seen widespread adoption and has been used by professionals worldwide to design and operate buildings and by researchers to predict thermal sensation.
        It is still currently used in its original form in the \gls{7730} although it has a low prediction accuracy, especially outside thermal neutrality.
        Several other formulations have been proposed to compensate for its limitations, one of which is currently used in the \gls{55}.
        \gls{7730} and \gls{55} are the most widely used thermal comfort Standards worldwide, and their differences are a source of confusion for users who find it difficult to decide which model to use.

        We aim to solve this problem by comparing the accuracy of the two main \ac{pmv} formulations, against \var{entries_db_used} thermal sensation votes collected in buildings.
        We found that the \ac{pmv-ce} has the same accuracy as the original \ac{pmv} in predicting thermal neutrality, despite its increased complexity and computational resources needed to calculate the results.
        Surprisingly, the bias of the \ac{pmv-ce} model was greater (a higher number is negative) than the \ac{pmv} when we only analyzed the entries with \ac{v}$\geq$\qty{0.2}{\m\per\sec}.
        % todo add values below and complete the Abstract
        The \ac{pmv} and \ac{pmv-ce} accuracy were XX\% and YY\% for $\mid$\ac{pmv}$\mid \leq 2$ and XX\% and YY\% for $\mid$\ac{pmv}$\mid \leq 1$, respectively.
        Neither PMV model could accurately predict `cold’, `cool’, `warm’, or `hot’ thermal sensations.
        Consequently, the PMV should only be used in conditions close to neutrality within the range $\mid$\ac{pmv}$\mid \leq 1$, and we suggest reducing the applicability limit of the Standards to this range.
    \end{abstract}

    \begin{keyword}
        Thermal comfort model \sep ISO 7730 \sep ASHRAE 55 \sep Thermal sensation \sep Accuracy
    \end{keyword}

>>>>

    \begin{abstract}
%        The \ac{pmv} model was developed by Fanger more than 50 years ago to predict the mean thermal sensation of a group of people.
%        It is based on a heat balance model of the human body.

%        Being relatively simple to calculate and being included in both the \gls{7730} and \gls{55} Standards, the \ac{pmv} has seen widespread adoption and has been used by professionals worldwide to design and operate buildings and by researchers to predict thermal sensation.
        The \ac{pmv} model, developed by Fanger, is still currently used in its original form in the \gls{7730} although it has a low prediction accuracy, especially outside thermal neutrality.
        Several other formulations have been proposed to compensate for its limitations, one of which is currently used in the \gls{55}.
        \gls{7730} and \gls{55} are the most widely used thermal comfort Standards worldwide, and their different \ac{pmv} formulations are a source of confusion for users who find it difficult to decide which model to use.

        We compared the accuracy of the two main \ac{pmv} formulations, against \var{entries_db_used} thermal sensation votes collected in buildings.
        We found that the use of the \ac{pmv-ce} provides no significant improvement over the original \ac{pmv} in predicting thermal sensation, despite its increased complexity and computational resources needed to calculate the results.
        Surprisingly, the bias of the \ac{pmv-ce} model was greater (a higher number is negative) than the \ac{pmv} when we only analyzed the entries with \ac{v}~$\geq$~\qty{0.2}{\m\per\sec}.

        We, therefore, recommend using the original \ac{pmv} instead of the \ac{pmv-ce}.
        In addition, we suggest reducing the applicability limit of the \ac{pmv} within the range $\mid$\ac{pmv}$\mid \leq 0.5$.
        This recommendation already aligns with the \gls{55} Standard's definition which states that the \ac{pmv} model can be used to determine ``the combinations of indoor thermal environmental factors and personal factors that will produce \textit{satisfactory thermal environmental conditions} for a majority of the occupants within the space''.
        The \ac{pmv} model cannot determine the degree by which people are dissatisfied.
        A value higher or lower than \num{.5} or \num{-.5}, respectively only indicates that people are on the `warm' or `cold' side.
        Finally, our results show that the classic assumption that people who are `slightly warm' or `slightly cool' are thermally comfortable leads to under-counting thermal discomfort in our dataset.
        We, hence, recommend in thermal comfort research the use of the thermal preference scale to determine how people perceive their thermal environment.
    \end{abstract}

    \begin{keyword}
        Thermal comfort model \sep ISO 7730 \sep ASHRAE 55 \sep Thermal sensation \sep Thermal preference
    \end{keyword}
